---
title: "Regressão Logistica"
output: pdf_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
knitr::opts_knit$set(root.dir = "D:\\Downloads\\")

# Helper packages
library(dplyr)     # for data wrangling
library(ggplot2)   # for awesome plotting
library(rsample)   # for data splitting

# Modeling packages
library(caret)     # for logistic regression modeling
library(mlbench)

# Model interpretability packages
library(vip)       # variable importance
```

## Base de dados para estudo
```{r }
dados = read.csv('default.csv', sep=';')
```
```{r }
summary(dados)
```

```{r }
plot(dados$glucose, diab$default)
```
  

```{r }
diab = na.omit(dados)
```

```{r }
summary(diab)
```

```{r }
pairs(diab)
```

##Fiting a simple model
```{r}
sim_model <- glm(diabetes ~ glucose, data = diab, family = binomial)
summary(sim_model)
```
```{r}
exp(sim_model$coefficients)
```

This indicate that one unit increase in the glucose concentration will increase the odds of being diabetes-positive by 1.04 times.

```{r}
confint(model1)
```


```{r}
y.pred.prob <- predict(sim_model,type = "response")
head(y.pred.prob)
```


```{r}
contrasts(diab$diabetes)
```
```{r}
y.pred.class <- ifelse(y.pred.prob > 0.5, "pos", "neg")
head(y.pred.class)
```



```{r}
set.seed(123)
cv_model1 <- train(
  diabetes ~ glucose, 
  data = diab, 
  method = "glm",
  family = "binomial",
  trControl = trainControl(method = "cv", number = 10)
)

set.seed(123)
cv_model2 <- train(
  diabetes ~ glucose + pressure, 
  data = diab, 
  method = "glm",
  family = "binomial",
  trControl = trainControl(method = "cv", number = 10)
)

set.seed(123)
cv_model3 <- train(
  diabetes ~ ., 
  data = diab, 
  method = "glm",
  family = "binomial",
  trControl = trainControl(method = "cv", number = 10)
)


```
```{r}
# extract out of sample performance measures
summary(
  resamples(
    list(
      model1 = cv_model1, 
      model2 = cv_model2, 
      model3 = cv_model3
    )
  )
)$statistics$Accuracy

```
```{r}
# predict class
pred_class <- predict(cv_model3, diab)

# create confusion matrix
confusionMatrix(
  data = pred_class, 
  reference = diab$diabetes
)

```

```{r}
# predict class
pred_class <- predict(cv_model3, diab)

# create confusion matrix
confusionMatrix(
  data = relevel(pred_class, ref = "pos"), 
  reference = relevel(diab$diabetes, ref = "pos")
)

```

No Information Rate: 0.6684. This represents the ratio of non-diabetic vs. diabetic in our training data. Consequently, if we simply predicted "Neg" for every patient we would still get an accuracy rate of 66.84%.


```{r}
library(ROCR)

# Compute predicted probabilities
m1_prob <- predict(cv_model1, diab, type = "prob")$pos
m3_prob <- predict(cv_model3, diab, type = "prob")$pos

# Compute AUC metrics for cv_model1 and cv_model3
perf1 <- prediction(m1_prob, diab$diabetes) %>%
  performance(measure = "tpr", x.measure = "fpr")
perf2 <- prediction(m3_prob, diab$diabetes) %>%
  performance(measure = "tpr", x.measure = "fpr")

# Plot ROC curves for cv_model1 and cv_model3
plot(perf1, col = "black", lty = 2)
plot(perf2, add = TRUE, col = "blue")
legend(0.8, 0.2, legend = c("cv_model1", "cv_model3"),
       col = c("black", "blue"), lty = 2:1, cex = 0.6)

```